Cosmological constraints from the redshift dependence of the volume effect: galaxy angular 2-point correlation function

### 2017-04-01 draft/draft1_cris.tex
updates

\shorttitle{Reshift Dependent Volume effect}
\shortauthors{X.-D. Li, C. Cheng, C. Park, C.G. Sabiu, H. Park, J. Kim, S.E. Hong}

@@

\title{Cosmological constraints from the redshift dependence of %geometric deformation
the galaxy angular 2-point correlation function}

@@

\author{Xiao-Dong Li, Changbom Park, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu, Hyunbae Park, }
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Cheng Cheng, }
\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
\affil{University of Chinese Academy of Sciences, P.R. China}
\author{Juhan Kim\altaffilmark{1},}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}

%\altaffiltext{1}{xiaodongli@kias.re.kr}
%\altaffiltext{2}{cbp@kias.re.kr}
%\altaffiltext{3}{csabiu@kasi.re.kr}
%\altaffiltext{4}{\bf Hyunbae: your email}
\altaffiltext{1}{Corresponding Author: Cris, Add your email!!!}

@@

\begin{abstract}
We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
to constrain cosmological parameters.
When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
As a result, we observe a redshift-dependent rescaling of the measured galaxy angular 2pCF.
We test our method on the Horizon Run 4 N-body simulation snapshot data, 
which contains hundreds of millions of galaxies at redshifts 
0, 0.5, 1, 1.5 and 2
We find the shape of angular 2pCF, as a function of scale,
exhibits evident redshift evolution when an incorrect set of cosmological parameters adopted,
and is relatively insensitive to the other effects such as gravitational growth of structure,
the galaxy bias, and the redshift-space distortion.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future large scale structure surveys, especially the photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \cite{Li2014,Li2015,Li2016},
which use a strategy to constraining cosmological parameters based on some redshift-invariant physical quantity;
they have a lot of merit,
e.g., lead to powerful constraints, are less affected by the systematic effects introduced by non-linear clustering or RSD,
do not require accurate analytical modeling of the galaxy correlation function,
are applicable on relatively small clustering scales,
and are applicable to many future LSS surveys.
\end{abstract}

@@

Various statistical methods have been proposed to measure these effects.
The AP effect can be measured through statistical study of the clustering of galaxies \citep{Ballinger1996,Matsubara1996}.
This method has been applied to a series of LSS surveys
\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
Alternative approaches uses the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
Methods proposed that are able to probe the volume effect include the number counting of 
galaxy clusters \citep{PS1974,VL1996} and topology \citep{topology},
the BAO scale \citep{EHT1998,BG03,SE03},
and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.

%\bibiem[Kazin et al (2012)]{KSB2012}
%Kazin, E.A., S\'{a}nchez, A.G., Blanton, M.R. 2012, MNRAS, 419, 3223

In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from the LSS data.
%proposed a series of methods to probe the geometric information encoded in the LSS data.
We found that the AP or volume effect in general introduces a geometric distortion that evolves significantly with redshift;
this phenomenon can be utilized to distinguish the AP effect from the other effects, such as the redshift-space distortion (RSD).
The radial distances of galaxies are inferred from the measured redshifts, which are distorted by the peculiar motion of galaxies, 
leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
This is the major systematic effect limiting our ability to probe the geometry of LSS from galaxy distribution.
We found its influence is significantly reduced when studying the redshift dependence of the distortion.

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the LSS distortion. 
We tested the idea on the Horizon Run 3 (HR3) N-body simulation \citep{horizonrun},
showing that the redshift evolution of the gradient field 
can be used to infer unbiased constraints on cosmological parameters and that it is, largely, insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the line of sight.
When an incorrect cosmological model is adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the comoving volume elements;
both effects have significant redshift dependence.
Although the RSD effect significantly distorts $\xi(\mu)$, 
it exhibits much less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
and we arrive at tight cosmological constraints competitive with mainstream probes of SNIa, BAO, CMB.

In this paper we continue our exploration of this strategy and presented 
a new method using the redshift of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology result in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\omega(r_{\bot})$.
The signal is sensitive to the cosmological parameters and relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to HR4 mock galaxies, using hundreds of millions of galaxies at redshifts $0\leq z\leq2$
and develop the statistical procedure to constrain cosmological parameters.

@@

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5,  \nonumber \noindent 
\end{eqnarray}
then the shapes of the squares appear distorted (AP effect),
and their sizes are wrongly estimated (volume effect).
Cosmological models (i,iii) yield to compressed size (in both angular and LOS direction),
and the degree of compression increases with increasing distance;
the situation is opposite for the other two cosmologies.

@@

%As will be introduced in the next section, 
%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
We take the snapshot data of the mock galaxies at $z=0,0.5,1,1.5,2$.
%We require subhalos to have at least 30 member particles, 
%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
we select 457, 406, 352, 206 and 228 million mock galaxies at the five redshifts,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in units of $ 10^{-2} h^{3} \rm Mpc^{-3}$
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.
Applying a uniform mass cut, at higher redshift we obtained a smaller number of galaxies with {\it larger bias}.

@@

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   \includegraphics[width=16cm]{fig2.eps}
   }
   \caption{\label{fig_scatter}
  The 2D distribution of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 mock galaxies, 
  at redshifts 0.5, 1, 1.5 and 2.
  Left and right panels show the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
  and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
  The growth of structure strengths the clustering and make structures more compact at lower redshift.
  When the wrong cosmology is adopted, the covmoving distances are mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$, respectively,  leading to a clear redshift evolution of the sizes of structures.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

Among different redshifts there is large variation in the amplitude of $\omega(r_\perp)$.
The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
The amplitude is highest at $z=0$ where the structures experienced the most growth.
$\omega(r_\perp)$ increases at $z>1$ with increasing redshift 
as a reason of increasing galaxy bias.
%leading to stronger clustering strength and higher amplitude of 2pCF.
%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
%The trend is different from $z=1,1.5,2$,
%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

@@

In order to directly compare the shape of the 2pCF at different redshifts,
in the middle panel of Figure \ref{fig_diffz} 
we show the $r_\perp\omega$ normalized by the overall amplitude within 
$5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
(here after $\hat \omega_{r_\perp}$):
\begin{equation}
 \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
\end{equation}
where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
Below $5 h^{-1}$ Mpc the non-linear growth of structure 
leads to systematic redshift evolution which could be difficult to be reliably accounted;
On scales larger than $40 h^{-1}$ Mpc,
the analytical modeling of the shape of the angular 2pCF is relatively well understood;
one can just fit the 2pCF with the theoretical predictions \citep{Salvador2014,Salvador2016} 
instead of using our method 
(although our method should also be applicable).

@@

Although the change of amplitude could be a more significant cosmological consequence 
than the alteration of shape,
it is mixed with the other effects; 
the growth of structure and a larger galaxy bias can also lead to a stronger clustering and thus an enhanced amplitude.
%it is more difficult to 
%But this phenomenon can also appear in case of gravitational growth of structure or increasing of bias,
%so we will not make use of it to do cosmological constraint.
In order to reliably extract the cosmological information, 
we just utilize the the redshift evolution of the 2pCF shape, 
which is less affected by other factors.
%which is as a signal suggesting that the assumed cosmological parameters are wrong.

@@

@@

We vary the mass cut and check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
The upper panels of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
are imposed to create samples with different galaxy bias.
The measured angular 2pCF are displayed.

Different mass cuts result in large variation in the amplitude of the 2pCF (left panel);
but the shape of the \scr{normalised} 2pCF remains less affected (middle panel).
Compared with the sample of $M>3\times 10^{11} M_{\odot}$,
samples with mass limits of $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$
have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$, 
while the change in the shape is only $0.5\%,\ 2\%$ and $4\%$, respectively.
The effect of galaxy bias becomes much less significant by utilizing the shape of the 2pCF rather than the amplitude.

@@

@@

The effect of RSD is much milder in this work. 
The angular positions of galaxies are not shifted by RSD at all;
the only effect of RSD enter in the procedure of 
splitting galaxies into redshift shells.
The galaxies observed in a survey are split into shells of subsamples, 
with different redshift ranges. So that we can get the 2pCF measurement at different redshfits.
RSD distorts the galaxy redshift and as a result some galaxies 
(especially those close to the boundaries of shells) are assigned to the wrong redshift shells.

@@

The lower panel of Figure \ref{fig_sys} shows how it affects on the 2pCF.
Comparing this plot with Figure \ref{fig_diffz} one can clearly see the effect of RSD.
The amplitude of the measured 2pCF is enhanced by $\sim 10\%$ when considering the RSD effect 
and the slop of $\hat\omega_{r_\perp}$ is suppressed.
But the redshift evolution of $\hat\omega_{r_\perp}$ is still small, remain $\lesssim4\%$ at $0.5\leq z \leq 2$.
So RSD should not very affect the application of our method as long as its redshift evolution is small;
the small effect of RSD can be precisely modeled by simulations and corrected.
%If looking at the redshift evolution,
%the curves $\hat{r_\perp\omega} - \hat{r_\perp\omega}(z=0)$ displayed in the right panel,
%they changed a lot compared with the case of no RSD effect (the right panel of Figure \ref{fig_diffz}),
%but do not become much larger. %But RSD effect does not introduce large redshfit evolution, although the shape of  is

Similar to RSD, redshift errors of galaxies
also results in fuzzy boundaries of shells and misclassification of galaxies.
This effect should be properly quantified when dealing with real observational data.

@@

>>>>

\shorttitle{Reshift Dependent Volume effect}
\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, C. Cheng, J. Kim, S.E. Hong}

@@

\title{Cosmological constraints from the redshift dependence of the volume effect: galaxy angular 2-point correlation function}

@@

\author{Xiao-Dong Li, Changbom Park, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu\altaffilmark{1}, Hyunbae Park, }
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Cheng Cheng, }
\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
\affil{University of Chinese Academy of Sciences, P.R. China}
\author{Juhan Kim,}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}

%\altaffiltext{1}{xiaodongli@kias.re.kr}
%\altaffiltext{2}{cbp@kias.re.kr}
%\altaffiltext{3}{csabiu@kasi.re.kr}
%\altaffiltext{4}{\bf Hyunbae: your email}
\altaffiltext{1}{Corresponding Author: csabiu@kasi.re.kr}

@@

\begin{abstract}
We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
to constrain cosmological parameters.
When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
As a result, we observe a redshift-dependent rescaling of the measured galaxy angular 2pCF.
Using mock galaxy catalogues (containing millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the angular 2pCF shape, as a function of scale,
is sensitive to the adopted cosmological parameters. 
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
However, it is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the effect of redshift space distortions.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities;
they are all powerful in constrain cosmology and have a lot of merits,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
does not require accurate modeling of galaxy clustering,
and are applicable on relative small clustering scales.
\end{abstract}

@@

Various statistical methods have been proposed to measure these effects.
The AP effect was first suggested to be measured through the anisotropic clustering of galaxies \citep{Ballinger1996,Matsubara1996}. Later, with the advent of large observational spectroscopic programs, this was applied to a series of LSS surveys
\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016}.
Although there have also been alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
Methods proposed to measure the volume effect include the number counting of 
galaxy clusters \citep{PS1974,VL1996}, the topology of LSS \citep{topology},
the BAO scale \citep{EHT1998,BG03,SE03},
and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.

In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from the LSS data.
%proposed a series of methods to probe the geometric information encoded in the LSS data.
We found that the AP or volume effect in general introduces a geometric distortion that evolves significantly with redshift;
this phenomenon can be utilized to distinguish the AP effect from the other effects, such as the redshift-space distortion (RSD).
The radial distances of galaxies are inferred from the measured redshifts, which are distorted by the peculiar motion of galaxies, 
leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
It is the major systematic effects limiting our ability to probe the geometry of LSS from the galaxy distribution.
However, we found that the influence of RSD is significantly reduced when we consider only the redshift dependence of the distortion.

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the LSS distortion. 
We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
showing that the redshift evolution of the gradient field 
can be used to infer unbiased constraints on cosmological parameters and that it is, largely, insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the angle between the connection of the galaxy pairs and the line of sight direction.
When an incorrect cosmological model is adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the comoving volume elements;
both effects have significant redshift dependence.
Although the RSD effect significantly distorts $\xi(\mu)$, 
it exhibits much less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
and we arrive at tight cosmological constraints competitive with mainstream probes of SNIa, BAO, CMB.

In this paper we continue our exploration of this strategy and present 
a new method using the redshift evolution of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology result in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\omega(r_{\bot})$.
The signal is sensitive to the cosmological parameters and relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to HR4 mock galaxies, using hundreds of millions of galaxies at redshifts $0\leq z\leq2$
and develop the statistical procedure to constrain cosmological parameters.

@@

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5,  \nonumber \noindent 
\end{eqnarray}
then the shapes of the squares appear distorted (AP effect),
and their sizes are wrongly estimated (volume effect).
Cosmological models (i,iii) result in compressed volume elements (in both angular and LOS direction),
and the degree of compression increases with increasing distance;
the situation is opposite for the other two cosmologies.

@@

%As will be introduced in the next section, 
%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
We take the snapshot data of the mock galaxies at $z=0,0.5,1,1.5,2$.
%We require subhalos to have at least 30 member particles, 
%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
we select 457, 406, 352, 306 and 228 million mock galaxies at the five redshifts,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in units of $ 10^{-2} h^{3} \rm Mpc^{-3}$
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.
Applying a uniform mass cut, at higher redshift we obtained a smaller number of galaxies with {\it larger bias}.

@@

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   \includegraphics[width=16cm]{fig2_0.eps}
   }
   \caption{\label{fig_scatter}
  The 2D distribution of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 mock galaxies, 
  at redshifts 0.5, 1, 1.5 and 2.
  Left and right panels show the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
  and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
  The growth of structure strengths the clustering and make structures more compact at lower redshift.
  When the wrong cosmology is adopted, the covmoving distances are mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$, respectively,  leading to a clear redshift evolution of the sizes of structures.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

Among the different redshift bins there is large variation in the amplitude of $\omega(r_\perp)$.
The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
The amplitude is highest at $z=0$ where the structures experienced the most growth.
$\omega(r_\perp)$ increases at $z>1$ with increasing redshift 
as a reason of increasing galaxy bias.
%leading to stronger clustering strength and higher amplitude of 2pCF.
%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
%The trend is different from $z=1,1.5,2$,
%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

@@

In order to directly compare the shape of the 2pCF at different redshifts,
in the middle panel of Figure \ref{fig_diffz} 
we show the $r_\perp\omega$ normalized by the overall amplitude within 
$5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
(here after $\hat \omega_{r_\perp}$):
\begin{equation}
 \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
\end{equation}
where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
Below $5 h^{-1}$ Mpc the non-linear growth of structure 
leads to systematic redshift evolution which could be difficult to be reliably accounted;
On scales larger than $40 h^{-1}$ Mpc,
the analytical modeling of the shape of the angular 2pCF is relatively well understood;
one can just fit the 2pCF with the theoretical predictions \citep{BCGS2001,Salvador2014,Salvador2016} 
instead of using our method 
(although our method should also be applicable).

@@

Although the change of amplitude could be a more significant cosmological consequence 
than the alteration of shape,
it is mixed with the other effects; 
the growth of structure and a larger galaxy bias can also lead to a stronger clustering and thus an enhanced amplitude.
%it is more difficult to 
%But this phenomenon can also appear in case of gravitational growth of structure or increasing of bias,
%so we will not make use of it to do cosmological constraint.
In order to reliably extract the cosmological information, 
we just utilize the redshift evolution of the 2pCF shape, 
which is less affected by other factors.
%which is as a signal suggesting that the assumed cosmological parameters are wrong.

@@

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
    \includegraphics[width=14cm]{fig5.eps}
   }
   \caption{\label{fig_cosmo}
    $\hat{\omega}_{r_\perp}$ (upper panels) and $\hat{\omega}_{r_\perp}(z=z_i) - \hat{\omega}_{r_\perp}(z=0)$ (lower panels) at several redshifts,
    for four wrong cosmologies.
    The redshift evolution of the angular 2pCF shape in these wrong cosmologies are detected at high CL.
   }
\end{figure*}

@@

We vary the mass cut and check the effect of galaxy bias on $\hat \omega_{r_\perp}$.
The upper panels of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
are imposed to create samples with different galaxy biases.
The measured angular 2pCF are displayed.

Different mass cuts result in large variation in the amplitude of the 2pCF (left panel);
but the shape of the normalised 2pCF remains less affected (middle panel).
Compared with the sample of $M>3\times 10^{11} M_{\odot}$,
samples with mass limits of $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$
have amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$, 
while the change in the shape is only $0.5\%,\ 2\%$ and $4\%$, respectively.
The effect of galaxy bias becomes much less significant by utilizing the shape of the 2pCF rather than the amplitude.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
   \includegraphics[width=12cm]{fig9.eps}
   }
   \caption{\label{fig_contours}
   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
   the method can lead to very tight cosmological constraint.
   }
\end{figure*}

@@

The effect of RSD is much milder in this work. 
The angular positions of galaxies are not shifted by RSD at all;
the only effect of RSD enter in the procedure of 
splitting galaxies into redshift shells.
The galaxies observed in a survey are split into shells of subsamples, 
with different redshift ranges. This allows us to obtain 2pCF measurement at various redshifts.
RSD distorts the galaxy redshift and as a result some galaxies 
(especially those close to the boundaries of shells) are assigned to the wrong redshift shells.

@@

The lower panel of Figure \ref{fig_sys} shows how it affects on the 2pCF.
Comparing this plot with Figure \ref{fig_diffz} one can clearly see the effect of RSD.
The amplitude of the measured 2pCF is enhanced by $\sim 10\%$ when considering the RSD effect 
and the slop of $\hat\omega_{r_\perp}$ is suppressed.
However, the redshift evolution of $\hat\omega_{r_\perp}$ remains small,  $\lesssim4\%$ at $0.5\leq z \leq 2$.
Therefore RSD should not significantly affect the application of our method, as long as its redshift evolution is small;
the small effect of RSD can be precisely modelled by simulations and corrected.
%If looking at the redshift evolution,
%the curves $\hat{r_\perp\omega} - \hat{r_\perp\omega}(z=0)$ displayed in the right panel,
%they changed a lot compared with the case of no RSD effect (the right panel of Figure \ref{fig_diffz}),
%but do not become much larger. %But RSD effect does not introduce large redshfit evolution, although the shape of  is

Similar to RSD, redshift errors of galaxies
also results in fuzzy boundaries of redshift shells
Thankfully, there are some methods for mitigating this effect in photometric surveys using pair-center binning \citep{2010MNRAS.407..520N}.

@@

\bibitem[Nock et al.(2010)]{2010MNRAS.407..520N} Nock, K., Percival, W.~J., \& Ross, A.~J.\ 2010, \mnras, 407, 520
